\chapter[Overview of the software product]{Product Overview}

In this chapter we will provide an overview of our developed product and implemented software.

The product we developed consists out of the virtual human, written in GOAL, an agent programming language for programming rational agents, and the connector that lets the agent connect to the Tygron Environment, written in Java. The connector makes sure that we can provide our agent with continually updated information from the Tygron Engine, which is connected to a session environment. This is needed for the agent to act and react on everything that happens in the environment.

The connector uses the Tygron SDK to return information from the Tygron Engine to the Tygron Environment. There are different kinds of objects and data in the environment which are collected in itemsets called MapLinks, these MapLinks can be added to a listener, which notifies the Tygron Environment when MapLinks have been updated. When the Tygron Engine has been modified it will return an updated itemset to the Tygron Environment. Another way the SDK has been utilized is by creating actions in the environment which call on usable actions in the SDK to manipulate the Tygron Engine. Through the connector the agent is provided useful information from the environment and it will take the relevant information into account to decide the best course of action in its current state.

All stakeholders have a set of indicators which are goals set for the stakeholder to achieve at the end of a session. It is the task of every agent to try and achieve these indicators. When a session is started in the Tygron Engine an agent can be added to this session. The moment the agent is added to the session it will start collecting all useful data it received from the environment. When all the necessary data has been inserted into the agent it will look at the data and derive its own decisions. If a decision leads to an action in the session then the session's data will change. These changes will be sent to the Tygron Environment which returns the information to the agent. When the agent receives this new data it will update its knowledge and develop new decisions according to its indicators. The agent will always run until the session is finished, because there is no guarantee that achieved indicators will be changed later on.

\newpage