\addcontentsline{toc}{chapter}{Introduction}
\chapter*{Introduction}
In the serious game for urban planning by Tygron, a company that focusses on serious games for urban planning, it is possible to look at possible solutions for problems in development projects in cities and villages. In this game there are certain stakeholders that are played by humans. These stakeholders all have different interests and goals that they will try to accomplish. What we want to achieve by working on this project is to replace human stakeholders by virtual humans that make use of automatic decision making. These virtual humans will be able to make well-informed decisions in the game, making it possible to run sessions of the game without all human stakeholders available.

The agent that we developed is designed to simulate human behaviour as accurately as possible. When there are no humans available at a certain point of time, an agent can just simply fill in the role. Eventually, it might be possible to not have to use humans anymore because agents might even be better at doing the job as they are not biased and can do computations faster.

Each group that is part of this project developed an agent for one of the five stakeholders in the game, so at the end of this project we can run all the agents in a session without the need of any humans.

In this report we will first give an overview of what we have developed. After this we will reflect on the product and process from a software engineering perspective. Then we will give an exact description of all the functionalities that our agent has, followed by an explanation of our interaction design. Eventually we will evaluate our product and describe our outlook on the project.
\newpage
