\addcontentsline{toc}{chapter}{Introduction}
\chapter*{Introduction}
This context project was essentially tantamount to a request from the company 'Tygron'. The main request was to substitute human players with artificial intelligence within the 'Tygron Engine'. 'Tygron' is the company that provided the 'Tygron Engine' which is a serious game for urban planning. This means that the game can be used to examine possible solutions for problems in development projects for cities and villages. In this game there are certain stakeholders that can be played by humans. For our project we have developed a scenario, a specific environment, with the following five stakeholders: 'Municipality', 'Private Housing Corporation', 'Facilities', 'DUWO' and 'TUDelft'. These stakeholders all have different interests and goals that they will try to accomplish. 

Initially, a total of five teams had to collaboratively come up with an interesting scenario within the 'Tygron Engine'. This scenario had to have enough possibilities for interaction and decision logic for each of the five stakeholders. 

Each of these five teams was requested to develop a virtual human to substitute the human player for a single stakeholder. This means that all five teams were essentially responsible for a single virtual human which, in conjunction, were expected to be able to play in our a game session without any human interference. 

Our team was responsible for the virtual human to play the 'Private Housing Corporation' stakeholder. Each virtual human is required to be capable of making human-like decisions in the game and accurately conform to their stakeholders' properties. 

In this report we will first give an overview of what we have developed. After this we will reflect on the product and process from a software engineering perspective. Then we will give an exact description of all the functionalities that our agent has, followed by an explanation of our interaction design. Eventually we will evaluate our product and describe our outlook on the project.
\newpage
